---
title: "Activity 4: Regular Expressions"
---

## Regular Expressions Activity

First, load the lyrics from class:

```{r}
lyrics <- c("But I would walk 500 miles",
            "Yeah, 360. When you're in the mirror, do you like what you see?", 
            "I have loved you for a 1000 years, I'll love you for a 1000 more",
            "Where 2 and 2 always makes a 5",
            "17-38, ay",
            "I'm so 3008, You so 2000 and late")
```

```{r}
str_view_all(lyrics, "500|1000|2|360|5|17|38|3008|2000")
```



## Regular Expressions

* `[:digit:]` is a particular [Character Class](https://stat.ethz.ch/R-manual/R-devel/library/base/html/regex.html)
* Character classes are a way of specifying that you want to match one of the following characters.

```{r}
str_view_all(lyrics, "[:digit:]")
```

------------------------------------------------------------------------

## Regular Expressions

::: {.nonincremental}

* `+` is a quantifier
    * `+`: One or more
    
:::

```{r}
str_view_all(lyrics, "[:digit:]+")
```


# Activity: Regular Expression Sleuthing

::: {.fragment}

In groups of 2 - 3, go through the next slides and make a "dictionary" of what you believe each of the regular expressions shown is doing, and how it does that. 

:::

## Regular Expressions

What does `{n}` do?

```{r}
str_view_all(lyrics, "[:digit:]{2}")
```


ANSWER:

------------------------------------------------------------------------

## Quantifiers: What does each of these do? 

Fill out what each of the quantifiers below does. Use the below code chunk to try them out. I got you started by doing 2 of them for you. 

ANSWER:

* `?`: 0 or 1
* `*`: 
* `+`: 1 or more
* `{n}`: 
* `{n,}`: 
* `{n,m}`: 



```{r}
str_view_all(lyrics, "[:alnum:]{4,}")
```


------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:alpha:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:upper:]")
```

ANSWER:


------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:alnum:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:punct:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:graph:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[:space:]")
```

ANSWER:

------------------------------------------------------------------------

## Character Classes

* Can also create your own.

* What pattern does this regexp match?

* why no colons on this one? 

```{r}
str_view_all(lyrics, "[aeiou]")
```

ANSWER:

------------------------------------------------------------------------

## Other Handy Regexps

* What pattern does this regexp match?

* Why do we need an extra `\`?

```{r}
str_view_all(lyrics, "\\d")
```

ANSWER:


------------------------------------------------------------------------

## Other Handy Regexps

* What pattern does this regexp match?

```{r}
str_view_all(lyrics, "\\W")
```

ANSWER:

------------------------------------------------------------------------

## Other Handy Regexps

* What pattern does this regexp match?

```{r}
str_view_all(lyrics, "Whe[:alpha:]+")
```

ANSWER:


------------------------------------------------------------------------

## Groups

* What pattern does this regexp match?

* What do you think "\\1" is doing

```{r}
str_view_all(lyrics, "(\\d)\\1")
```



ANSWER:


------------------------------------------------------------------------

## Groups

* What pattern does this regexp match?

```{r}
str_view_all(lyrics, "(\\d)\\1\\1")
```

ANSWER:


------------------------------------------------------------------------

## Groups

* What pattern does this regexp match?

```{r}
str_view_all(lyrics, "([:alnum:])(\\s)[:alnum:]+\\2\\1")
```

ANSWER:


------------------------------------------------------------------------

## Other Handy Regexps

* What pattern does this regexp match?

```{r}
str_view_all(lyrics, "\\b")
```

ANSWER:

------------------------------------------------------------------------

## Anchors

* What pattern does this regexp match?

* What do you think the "^" is doing? 

```{r}
str_view_all(lyrics, "^\\d+")
```

ANSWER:


------------------------------------------------------------------------

## Anchors

* What pattern does this regexp match?

* What do you think the "$" is doing?

```{r}
str_view_all(lyrics, "\\d+$")
```

ANSWER:

------------------------------------------------------------------------

## Alternates

* What pattern does this regexp match?

* What is the "^" doing now? Hint: It is different than before. 

```{r}
str_view_all(lyrics, "[^aeiou]")
```

ANSWER:

------------------------------------------------------------------------

## Alternates

* What pattern does this regexp match?

```{r}
str_view_all(lyrics, "[0-2]0")
```

ANSWER:


------------------------------------------------------------------------

## Look Arounds

```{r}
str_view_all(lyrics, "(?<=\\d )[:alpha:]+")
```

ANSWER:

------------------------------------------------------------------------

## Look Arounds

```{r}
str_view_all(lyrics, "[:alpha:]+(?= \\d+)")
```

ANSWER:






